ASHA 2023 Listening Effort Data Analysis

### 2023-10-26 ASHA 2023 Analysis/data_analysis.Rmd
Counted number of accurate responses

# Selecting relevant variables to explore phrase accuracy and perceived listening effort
data1 <- data %>%
  dplyr::select(subject, trial, speaker, effort_rating, rep_acc) %>%
  dplyr::distinct()

>>>>

# Selecting relevant variables to explore phrase accuracy and perceived listening effort
data1 <- data %>%
  dplyr::select(subject, trial, speaker, effort_rating, rep_acc) %>%
  dplyr::distinct() %>%
  # removing trials with missing rep accuracy: 3 trials removed
  dplyr::mutate(rep_acc = ifelse(rep_acc == "", NA, rep_acc)) %>%
  dplyr::filter(!is.na(rep_acc))
